Formalizing Stack Safety as a Security Property

### 2022-12-07 submission5/core.tex
Wordsmithing

To characterize this situation in a property, we define a state element to be \emph{irrelevant}
if its value can be replaced with another value without changing the observable behavior
of the machine. This replacement value must respect any enforcement-relevant constraints on
values; in the tagged setting, we define two values as variants if they share the same tag
component. Then, for a set of elements \(\components\),
a pair of states \(\mach\) and \(\nach\) are {\em \(\components\)-variants} if
they agree on the value of every element not in \(\components\), and the values
in all elements are variants.

The elements of \(\components\) are \emph{irrelevant}
in \(\mach\) if every \(\components\)-variant state produces an equivalent observation trace
(see Section \ref{sec:events}); all other elements are \emph{relevant}.
We characterize \emph{observational integrity} as the property that
every relevant element that is \(\sealed\) under the callee's view is restored
to its original value at the return point.

>>>>

To characterize this situation in a property, we use the concept of {\it non-interference}
based on variant states. Specifically, we consider two values to be variants, even if their
payload values differ, as long as the remainder of their state respects other system-specific
constraints; in the case of the tagged system, the tag component must be identical.
Then, for a set of elements \(\components\),
a pair of states \(\mach\) and \(\nach\) are {\em \(\components\)-variants} if
they agree on the value of every element not in \(\components\), and the values
in \(\components\) are variants.

We say that the elements of \(\components\) are \emph{irrelevant}
in \(\mach\) if every \(\components\)-variant state produces an equivalent observation trace
(see Section \ref{sec:events}); all other elements are \emph{relevant}.
We characterize \emph{observational integrity} as the property that
every relevant element that is \(\sealed\) under the callee's view is restored
to its original value at the return point.
